Remotely SST

### 2019-08-06 remote_SST.Rmd
updated

PN_MCS_events <- MCS_func(df = PN_MCS)
LB_MCS_events <- MCS_func(df = LB_MCS)
SB_MCS_events <- MCS_func(df = SB_MCS)
SP_MCS_events <- MCS_func(df = SP_MCS)

HB_MCS_events <- detect_event(HB_MCS, coldSpells = TRUE) 
```

@@

PN_upwell_events <- MCS_func(df = PN_upwell)
LB_upwell_events <- MCS_func(df = LB_upwell)
SB_upwell_events <- MCS_func(df = SB_upwell)
SP_upwell_events <- MCS_func(df = SP_upwell)

HB_upwell_events <- detect_event(HB_upwell, minDuration = 2, coldSpells = TRUE)
```

@@

PN_MCS_events <- MCS_func(df = PN_MCS)
LB_MCS_events <- MCS_func(df = LB_MCS)
SB_MCS_events <- MCS_func(df = SB_MCS)
SP_MCS_events <- MCS_func(df = SP_MCS)

HB_MCS_events <- detect_event(HB_MCS, coldSpells = TRUE) 
```

>>>>

PN_MCS_events_MUR <- MCS_func(df = PN_MCS)
LB_MCS_events_MUR <- MCS_func(df = LB_MCS)
SB_MCS_events_MUR <- MCS_func(df = SB_MCS)
SP_MCS_events_MUR <- MCS_func(df = SP_MCS)

HB_MCS_events_MUR <- detect_event(HB_MCS, coldSpells = TRUE) 
```

@@

PN_upwell_events_MUR <- MCS_func(df = PN_upwell)
LB_upwell_events_MUR <- MCS_func(df = LB_upwell)
SB_upwell_events_MUR <- MCS_func(df = SB_upwell)
SP_upwell_events_MUR <- MCS_func(df = SP_upwell)

HB_upwell_events_MUR <- detect_event(HB_upwell, minDuration = 2, coldSpells = TRUE)
```

@@

PN_MCS_events_CMC <- MCS_func(df = PN_MCS)
LB_MCS_events_CMC <- MCS_func(df = LB_MCS)
SB_MCS_events_CMC <- MCS_func(df = SB_MCS)
SP_MCS_events_CMC <- MCS_func(df = SP_MCS)

HB_MCS_events_CMC <- detect_event(HB_MCS, coldSpells = TRUE) 
```

```{r}
upwell_func <- function(df){
  res_clim <- ts2clm(df, climatologyPeriod = c("1991-09-01", "2015-12-30"),
                   pctile = 30)
  return(res_clim)
}

PN_upwell <- upwell_func(df = CMC_PN)
LB_upwell <- upwell_func(df = CMC_LB)
SB_upwell <- upwell_func(df = CMC_SB)
SP_upwell <- upwell_func(df = CMC_SP)

HB_upwell <- ts2clm(CMC_HB, climatologyPeriod = c("2002-06-01", "2005-10-19"), # Climatological period differs to the rest
                   pctile = 10)

PN_upwell_events_CMC <- MCS_func(df = PN_upwell)
LB_upwell_events_CMC <- MCS_func(df = LB_upwell)
SB_upwell_events_CMC <- MCS_func(df = SB_upwell)
SP_upwell_events_CMC <- MCS_func(df = SP_upwell)

HB_upwell_events_CMC <- detect_event(HB_upwell, minDuration = 2, coldSpells = TRUE)
```
